\documentclass[12pt]{article}
%\documentclass{article}
\usepackage[
  letterpaper,
  margin=1in,
  headsep=4pt, % separation between header rule and text
]{geometry}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{tgschola}
\usepackage{lastpage}
\usepackage{setspace}
\renewcommand{\baselinestretch}{1.2}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{%
  \footnotesize\sffamily
  \yourname\quad
  web: \textcolor{black}{\itshape\yourweb}\quad
  \textcolor{black}{\youremail}}
% \fancyfoot[C]{Page \thepage\ of \pageref{LastPage}}

\newcommand{\soptitle}{Personal Statement}

\newcommand{\yourname}{Wang Xuezhong}
\newcommand{\youremail}{OceanWong1991@gmail.com}
\newcommand{\yourweb}{https://oceanwong1991.github.io/}

\newcommand{\statement}[1]{\par\medskip
  \underline{\textcolor{black}{\textbf{#1:}}}\space
}

\usepackage[
  colorlinks,
  breaklinks,
  pdftitle={\yourname - \soptitle},
  pdfauthor={\yourname},
  unicode
]{hyperref}

\setlength{\parindent}{0pt}
\begin{document}

\begin{center}\LARGE\soptitle\\
\large \yourname\ (Computer Science (MSc) applicant for Sep---2022)
\end{center}

\hrule
\vspace{1pt}
\hrule height 1pt


\sffamily
\mdseries



\bigskip

Working in the information technology industry for more than 6 years. I am writing to apply for the Master's degree in Computer Science technology study at your honored university, in the hope of keeping abreast with the latest professional information and skills.

\bigskip

\statement{Theoretical and Practical Experience in IT Industry}
Having a period of precious work experience is one of my greatest assets. Upon graduation, I became an Android software engineer in a startup. After a year of hard work, I could develop programs independently without any difficulty. So I decided to challenge myself to do something further and difficult, and I started self-education in artificial intelligence; In the beginning, I hardly know anything about this area, but I know Artificial Intelligence is amazing, There were so many reports and information on newspaper and internet, and said AI will change the world, will provide every child with personalized education, and make inexpensive self-driving cars to all. So I was excited just thinking about it! 

\bigskip

I remember the first course I was taking is Stanford university's Machine learning which was instructed by professor Andrew Ng, this course is really great, from which I learnt lots of basic knowledge about machine learning algorithm and neural network. I think the great part is the discussion Forum. I remember after every week's learning, we would have programming exercises, at first, I was not familiar with Matlab, not to mention matrix operation by Matlab and I felt very frustrated. I didn't know how to finish my exercises, So I went to Discussion Forums to find some clues, To my surprise, There were many students issues on the forum, if you didn't find an answer to your problem you can open new a thread, then people who know about it will answer it. I enjoy discussing with others from which I got different views about the same question. it also broadens my horizons and enables me to make friends with different students from a different culture. At the end of this lesson, I Achieved Grade: 95\%, then I attended Johns Hopkins University's Mathematical Biostatistics Boot course, and Achieved Grade: 86\%, Such an experience not only enabled me to assimilate the essence of the courses directly but also substantially improved my command of English language, especially the language and the vocabulary as used in computer science.

\bigskip

After two years of learning, I wanted to test my abilities. I attended the competition at Kaggle. The first competition which I attended is APTOS 2019 Blindness Detection. There were about 3,500 competitors from all over the world paticipated in this competition, The first thing I need do is to design a neural network, I didn't want to train a model from start, Training a model from start is a time-consuming thing, also it will waste a lots of electricity, So I used tranfer learning strategy, I took efficientnet B0 as my basic network, then frozened all layers except last fully connect layer; changed loss fuction to MSELoss, and used Adam as a optimizer; after 10 hours training, I saw the loss is converging; then I submmited my result, Just as I thought, I didn't enter medal pool, I need to change my strategy, I did a lots of experiences, including data preprocessing(crop image), data augementation(random crop, rotation, clathe, contrast, brightness...), use different model(EfficientNet-B2, EfficientNet-B3, resnet),  5-fold CV, TTA(test time augmentation), ensemble model(different weight on the results of different model), during this time, I was obessed with this competition; I had a lot of ideas, and it is easay to put my thoughts into prectice, then got the result, I would be glad if I enter the medal pool. I spent lots of time and energy on that project. finally, the result was great! As a solo participant, I got my first silver medal(Top 2\%(55/2928)). Then I took part in two competitions at Kaggle, Got another silver medal(Top 6\%(30/546)). And I successfully got Competition Expert Tier. TOP 0.67\%(1072/159,193)

\bigskip

After that competitions, I focus on the company's projects; As a team leader, I completed the project of Blind Spot Detection and Driver Status Monitor.

\bigskip

My work experience is valuable in that it has enabled me to accumulate ample empirical wealth and has provided important groundwork for undertaking higher-level research in computer science.

\bigskip

\statement{Study Plan in CA}
In the field of Computer Science, I am still a relative novice. I feel it necessary for me to go back to university to receive advanced training and systematic education. Out of such a consideration, I think The Master of Computer Science at the University of Victoria is my first choice, for its unceasing efforts to cultivate experts in the field of Computer Science. To prepare me fully for further study, I have made an academic plan based on the current development of my knowledge. I intend to consolidate my foundation in Computer Science in a systematic way, Learning core courses; Participating in projects, broadening my horizons in the application of Artificial intelligence with the Design and Engineering of Intelligent Systems, and preparing myself for the growing demand for computer science. 

\bigskip

\statement{Future Plan}
After graduating, I intend to bring what I have learnt at the University of Victoria into the industry, turning cutting-edge Computer Science technologies into pragmatic products. Given the program's prestige, I believe finding employment will no doubt be little trouble. I would like to seek a position as an AI engineer at a famous company, like Google, Tencent. I can utilize my talent in Artificial intelligence to fulfil my dream of making a more intelligent system to improves every person's life.

\bigskip

With all the research I have done, I am fully convinced that the Master of Computer Science at the University of Victoria is the ideal program to allow me to realize my full potential.

\end{document}
