\documentclass[12pt]{article}
%\documentclass{article}
\usepackage[
  letterpaper,
  margin=1in,
  headsep=4pt, % separation between header rule and text
]{geometry}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{tgschola}
\usepackage{lastpage}
\usepackage{setspace}
\renewcommand{\baselinestretch}{1.2}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{%
  \footnotesize\sffamily
  \yourname\quad
  web: \textcolor{black}{\itshape\yourweb}\quad
  \textcolor{black}{\youremail}}
% \fancyfoot[C]{Page \thepage\ of \pageref{LastPage}}

\newcommand{\soptitle}{Personal Statement}

\newcommand{\yourname}{Xuezhong Wang}
\newcommand{\youremail}{OceanWong1991@gmail.com}
\newcommand{\yourweb}{https://oceanwong1991.github.io/}

\newcommand{\statement}[1]{\par\medskip
  \underline{\textcolor{black}{\textbf{#1:}}}\space
}

\usepackage[
  colorlinks,
  breaklinks,
  pdftitle={\yourname - \soptitle},
  pdfauthor={\yourname},
  unicode
]{hyperref}

\setlength{\parindent}{0pt}
\begin{document}

\begin{center}\LARGE\soptitle\\
\large \yourname\ (Master of Applied Data Science (MADS) applicant for July---2023)
\end{center}

\hrule
\vspace{1pt}
\hrule height 1pt


\sffamily
\mdseries



\bigskip

 Having Worked in the information technology industry for more than 6 years, I am writing to apply for the Master of Applied Data Science at your prestigous university, in the hope of keeping abreast with the latest professional information and skills.

\bigskip

\statement{Theoretical and Practical Experience in IT Industry}

”In God we trust. All others must bring data.” This quote, made by W. Edwards Deming, refers mainly to the importance of data measurement and analysis. Data Science is a key element when working with AI, Monitoring and Automation. Using Data Science to analyze and group data, create correlations, look for clusters and essentially gain insights into data.

\bigskip

Over the years, I have gained considerable technical expertise from my rich work experience. Upon graduation, I became an Android software engineer in a startup. After a year of hard work, I could develop programs independently without any difficulty. So I decided to challenge myself to do something further and difficult, and I started self-education in data science and artificial intelligence. In the beginning, I hardly know anything about this area, but I know Artificial Intelligence is amazing. There were so many reports and information on newspaper and internet, and said AI will change the world, will provide every child with personalized education, and make inexpensive self-driving cars to all. So I was excited just thinking about it! 



I remember the first course I took was Stanford university's \textit{M}achine learning which was instructed by professor Andrew Ng, from which I learnt lots of basic knowledge about machine learning algorithm and neural network. I think the greatest part is the discussion forum. After every week's learning, we would have programming exercises. At first, I was not familiar with Matlab, not to mention matrix operation by Matlab and I felt very frustrated. I didn't know how to finish my exercises, So I went to Discussion Forums to find some clues, To my surprise, I was not alone, there were many others facing similar issues. It was so fascinating to communicate with like-minded people and learn from each other. If you didn't find an answer to your problem you can open new a thread, then people who know about it will answer it. I enjoy discussing with others from which I got different views about the same question. it also broadens my horizons and enables me to make friends with different students from a different culture. At the end of this lesson, I Achieved Grade: 95\%, then I attended Johns Hopkins University's Mathematical Biostatistics Boot course, and Achieved Grade: 86\%, Such experiences not only enabled me to assimilate the essence of the courses directly but also substantially built on my vocabulary in computer science  and computing-related fileds.

\bigskip

After two years of learning, I wanted to test my abilities. I attended the competition at Kaggle(tthe biggest online community of data scientists and machine learning practitioners in the world). The first competition which I attended was APTOS 2019 Blindness Detection. about 3,500 competitors from all over the world paticipated in this competition, The first thing I needed do was to design a neural network, I didn't want to train a model from start. Training a model from start is time-consuming, also it will waste a lots of electricity. So I used tranfer learning strategy, I took efficientnet B0 as my basic network, then frozened all layers except last fully connect layer; changed loss fuction to MSELoss, and used Adam as a optimizer; after 10 hours training, I saw the loss is converging; then I submmited my result, Just as I thought, I didn't enter medal pool, I need to change my strategy, I did a lots of experiences, including data preprocessing(crop image), data augementation(random crop, rotation, clathe, contrast, brightness...), use different model(EfficientNet-B2, EfficientNet-B3, resnet),  5-fold CV, TTA(test time augmentation), ensemble model(different weight on the results of different model), during this time, I was obessed with this competition; I had a lot of ideas, and it is easay to put my thoughts into prectice, then got the result, I would be glad if I enter the medal pool. I spent lots of time and energy on that project. finally, The result turned out to be great. As a solo participant, I got my first silver medal(Top 2\%(55/2928)). Then I took part in two competitions at Kaggle, Got another silver medal(Top 6\%(30/546)). And I successfully got Competition Expert Tier. TOP 0.67\%(1072/159,193)

\bigskip

After that competition, I focused on the company's projects; As a team leader, I completed the project of Blind Spot Detection and Driver Status Monitor.

\bigskip

My work experience is valuable in that it has enabled me to accumulate ample empirical wealth and has provided important groundwork for undertaking higher-level research in computer science.

\bigskip

\statement{Study Plan in NZ}
In the field of Data Science, I am still a relative novice. I feel it necessary for me to go back to university to receive advanced training and systematic education. Out of such a consideration, I think Master of Applied Data Science at the University of Canterbury is my first choice, for its unceasing efforts to cultivate experts in the field of Data Science. To prepare me fully for further study, I have made an academic plan based on the current development of my knowledge. I intend to consolidate my foundation in Data Science in a systematic way, Learning core courses; Participating in projects, broadening my horizons in the application of Data Science with the Design and Engineering of Intelligent Systems, and preparing myself for the growing demand for computer science. 

\bigskip

\statement{Future Plan}
After graduating, I intend to bring what I have learnt at the University of Canterbury into the industry, turning cutting-edge Computer Science technologies into pragmatic products. Given the program's prestige, I believe finding employment will no doubt be little trouble. I would like to seek a position as a Data analyst at a famous company, like Google, Tencent. I can utilize my talent in Data Science to fulfil my dream of making a more intelligent system to improves every person's life.

\bigskip

With all the research I have done, I am fully convinced that the Master of Applied Data Science at the University of Canterbury is the ideal program to allow me to realize my full potential.

\end{document}
