\documentclass{article}
\usepackage[
  letterpaper,
  margin=1in,
  headsep=4pt, % separation between header rule and text
]{geometry}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{tgschola}
\usepackage{lastpage}
\usepackage{setspace}
\renewcommand{\baselinestretch}{1.5}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{%
  \footnotesize\sffamily
  \yourname\quad
  web: \textcolor{black}{\itshape\yourweb}\quad
  \textcolor{black}{\youremail}}
% \fancyfoot[C]{Page \thepage\ of \pageref{LastPage}}

\newcommand{\soptitle}{Personal Statement}

\newcommand{\yourname}{Ocean Wong}
\newcommand{\youremail}{OceanWong1991@gmail.com}
\newcommand{\yourweb}{https://oceanwong1991.github.io/}

\newcommand{\statement}[1]{\par\medskip
  \underline{\textcolor{black}{\textbf{#1:}}}\space
}

\usepackage[
  colorlinks,
  breaklinks,
  pdftitle={\yourname - \soptitle},
  pdfauthor={\yourname},
  unicode
]{hyperref}

\begin{document}

\begin{center}\LARGE\soptitle\\
\large of \yourname\ (DS Master applicant for Feb---2022)
\end{center}

\hrule
\vspace{1pt}
\hrule height 1pt

\bigskip

Working in the information technology industry for more than 6 years. I am writing to apply for the Master's degree in data science technology study at your honored university, in the hope of keeping abreast with the latest professional information and skills.

\statement{Theoretical and Practical Experience in IT Industry}
Having a period of precious work experience is one of my greatest assets. Upon graduation, I became an Android software engineer in a startup. After a year's hard work, I felt free to develop Android applications, So, I decided to challenge myself to do something further and difficult
I started self-education in artificial intelligence; In the beginning, I hardly know anything about this area, but I know Artificial Intelligence is amazing, There are so many reports and information on newspaper and internet say AI will change the world, provide every child with personalized education, and make inexpensive self-driving cars to all. So I was excited just thinking about it! 


On that day, I opened my account on Coursera, and started my journey to AI; The first course I chose is Stanford university's Machine learning which was instructed by professor Andrew Ng, this course is really great, from which I learnt lots of basic knowledge about machine learning algorithm and neural network. I think the great part is Discussion Forums. I remember after every week's learning, we will have programming exercises, at first, I am not familiar with Matlab, not to mention matrix operation by Matlab and I felt very frustrated. I didn't know how to finish my exercises, So I went to Discussion Forums to find some clues, To my surprise, There were many students issues on the forum, if you didn't find an answer to your problem you can open new a thread, then people who know about it will answer it. I enjoy discussing with others from which I got different views about the same question. it also broadens my horizons and enables me to make friends with different students from a different culture. At the end of this lesson, I Achieved Grade: 95\%, then I attended Johns Hopkins University's Mathematical Biostatistics Boot course, and Achieved Grade: 86\%, Such an experience not only enabled me to assimilate the essence of the courses directly but also substantially improved my command of English language, especially the language and the vocabulary as used in computer science.



After two years of learning, I wanted to test my abilities. I attended the competition at Kaggle. The first competition which I attended is APTOS 2019 Blindness Detection. There were about 3,500 competitors from all over the world paticipated in this competition, The first thing I need do is to design a neural network, I didn't want to train a model from start, Training a model from start is a time-consuming thing, also it will waste a lots of electricity, So I used tranfer learning strategy, I took efficientnet B0 as my basic network, then frozened all layers except last fully connect layer; changed loss fuction to MSELoss, and used Adam as a optimizer; after 10 hours training, I saw the loss is converging; then I submmited my result, Just as I thought, I didn't enter medal pool; I need change my strategy, I did a lots of experiences, including data preprocessing(crop image), data augementation(random crop, rotation, clathe, contrast, brightness...), use different model(EfficientNet-B2, EfficientNet-B3, resnet),  5-fold CV, TTA(test time augmentation), ensemble model(different weight on the results of different model), during this time, I was obessed with this competition; I had a lot of ideas, and it is easay to put my thoughts into prectice, then got result, I will be glad if I enter the medal pool. I spent lots of time and energy on that project. finally, the result was great! As a solo participant, I got my first silver medal(Top 2\%(55/2928)). Then I took part in two competitions at Kaggle, Got another silver medal(Top 6\%(30/546)). Then I successfully got Competition Expert Tier. TOP 0.67\%(1072/159,193)

After that competitions, I was focus on the company's projects; As a team leader, I completed the project of Blind Spot Detection and Driver Status Monitor.

My work experience is valuable in that it has enabled me to accumulate ample empirical wealth and has provided important groundwork for undertaking higher-level research in computer science.

\statement{Study Plan in NZ}

In the field of Data Science, I am still a relative novice.  I feel it necessary for me to go back to university to receive advanced training and systematic education. Out of such a consideration, I think The Master of Data Science at Auckland University is my first choice, for its unceasing efforts to cultivate experts in the field of Data Science. To prepare me fully for further study, I have made an academic plan based on the current development of my knowledge. I intend to consolidate my foundation in Data Science in a systematic way, Learning core courses such as Advanced Data Science Practice and Data mining and Machine Learning; broadening my horizons in the application of Machine Learning with Design and Engineering of Intelligent Info Systems,  and preparing myself for the growing demand for data mining and Analysis. There are Over twenty elective courses with excellent CS-related resource on offer at Auckland University, I will seek to enrich my knowledge and improve my background further by taking Advanced Topics in Artificial Intelligence, Scheduling and Optimisation in Decision Making and Data Mining and Big Data.

\statement{Future Plan}

After graduating, I intend to bring what I have learnt at Auckland University into the industry, turning cutting-edge Data Science technologies into pragmatic products. Given the program's prestige, I believe finding employment will no doubt be little trouble. I would like to seek a position as a data analyst at a famous company, like Google, Tencent. I can utilize my talent in Machine Learning to fulfil my dream of making a more intelligent system to improves every person's life.

With all the research I have done, I am fully convinced that the Master of Data Science at Auckland University is the ideal program to allow me to realize my full potential.

\end{document}
