\documentclass[12pt]{article}
\usepackage[
  letterpaper,
  margin=1in,
  headsep=4pt, % separation between header rule and text
]{geometry}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{tgschola}
\usepackage{lastpage}
\usepackage{setspace}
\renewcommand{\baselinestretch}{1.2}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{%
  \footnotesize\sffamily
  \yourname\quad
  web: \textcolor{black}{\itshape\yourweb}\quad
  \textcolor{black}{\youremail}}
% \fancyfoot[C]{Page \thepage\ of \pageref{LastPage}}

\newcommand{\soptitle}{Statement Of Intent}

\newcommand{\yourname}{Xuezhong Wang}
\newcommand{\youremail}{OceanWong1991@gmail.com}
\newcommand{\yourweb}{https://oceanwong1991.github.io/}

\newcommand{\statement}[1]{\par\medskip
  \underline{\textcolor{black}{\textbf{#1:}}}\space
}

\usepackage[
  colorlinks,
  breaklinks,
  pdftitle={\yourname - \soptitle},
  pdfauthor={\yourname},
  unicode
]{hyperref}

\setlength{\parindent}{0pt}
\begin{document}

\begin{center}\LARGE\soptitle\\
\large \yourname\ (Computer Science (MSc) applicant for Sep---2022)
\end{center}

\hrule
\vspace{1pt}
\hrule height 1pt

\sffamily
\mdseries

\bigskip


My name is Xuezhong Wang, I am particularly passionate about Artificial Intelligence, VR especially metaverse. and I strongly believe that the metaverse is the next generation of the internet. As computers are getting better at gesture recognition, which will enable us to interact more naturally with computers, and eventually interpret and understand emotion and body language. AI plays an important role in this process. For example, Virtual reality needs to render the best information where your eyes is focused. AI can be used to predict where your eyes will look next, even through blinking, to help prepare the best rendering in advance. This is important for delivering the most immersive experience. At the same time, I think the ultimate interface should be personalized, and AI could make it possible. because everyone’s brain is different, the role of AI is to learn from and adapt to the uniqueness of each individual. When it comes to the rendering, I believe the next generation of AI models will be capable of editing and generating images in response to text input, and hopefully, they will understand the text better because of the many images they have seen and more powerful chips they could use. Finally, Artificial intelligence will power conversations, emotions, behaviors of characters you'll meet and even befriend in the metaverse.

\bigskip

I am looking forward to the possibility of working with professor Brandon Haworth, who works within the broad areas of Artificial Intelligence, Virtual Reality, Game Design and Development and Human-Computer Interaction. He also encourages applicants from different backgrounds and abilities. I am confident that my learning and work experience matches his expectations very well, I got my B.S. degree in Information and Computing Science in June 2015 at HBAU. After graduation, I worked as an Android software engineer in a startup. After one year's hard work, I can develop programs independently without any difficulty, Thus, I decided to challenge myself by trying something more difficult. My commitment, learning ability and result-oriented strategy enable me to be a successful AI engineer after consistent self learning. I have more than four years of experience in Machine Learning, Deep Learning, and Computer Vision, and experience in handling a variety of projects from concept to completion. During my 3 years leadership in my team, I have thoroughly demonstrated my strong communication, problem solving and cooperation skills. Our team completed a variety of projects successfully and received much recognition from colleagues. Our ADAS projects, like LCA and BSD, have achieved great success in the market and have been exported overseas.


\bigskip

In my opinion, the metaverse is a multi-disciplinary area, which requires knowledge of game design, game theory, behavioral pattern, databases, music, AI, GPUs, graphics, user experience design, storytelling, software engineering and a hundred other talents. I am excited about working with professor Brandon and committing my passion and intelligence to this promising area which is full of infinite possibilities.


\bigskip

Thank you for your consideration!


\end{document}


